---
title: "Inequality Demonstrated in U.S. Incarceration Rate"
author: "Simon Wang"
date: '2022-11-21'
output: html_document
---

```{r echo=FALSE, eval=TRUE, message=FALSE}
source("../source/a4-helpers.R")
source("../source/analysis.R")
```

## Abstract
This assignment analyzes the data collected by jkangbrown. It reorganizes the
originally faulty and incomplete data in such a way that it can be evaluated
validly. This compares the incarceration rate of different ethnecities of people
in states.

As you know, this is a markdown report. The [R Markdown Cheatsheet](https://www.rstudio.com/wp-content/uploads/2015/02/rmarkdown-cheatsheet.pdf) is **useful!**

* Here's a test of a dynamic variable. Say **"`r q1_string`!!!**
* Here's another test. A vector
of numbers: `r test_query2(num)`.

Recall that _{r echo=TRUE}_ can be used to display the code,
which is very useful when developing and debugging a report. Here's an example:

```{r echo=TRUE}
num <- 5
sum <- sum(test_query2(num))
print(sum)
```

## Introduction
Racism has been a long-lasting and despairing issue in the United States, and
it is apparent in its incarceration rate. Prejudice both inherent and constitutive
runs rampant in our criminal justice system. This data can be used to find
regions that have disproportionately high incarceration rate for America's
black population, or just incarceration rate in generation.
A direct stakeholder for this data is the BIPOC population of the United
States; they are directly damaged by the unjust criminal justice system. An
indirect stakeholder for this could be law enforcers and politicians, whose
work will be affected the state of the citizens and whose votes will be impacted
by the illuminating the unjust system through this data.

## Data Summary


[TODO ... other sections ... See Canvas for details]

_All the very best with your work!_
